The serious gap laying on healthcare system in Thailand^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]

### 2022-04-05 outputs/paper/paper.Rmd
appendix session deleted
discussion section update

## From results of analysis, what should be enhanced?
It clearly shows that Thailand, especially in the rural regions in 1987 required more health care infrastructure. As WHO reported that the Thailand government started investing more on primary health care services in the rural area in the 1980s, we expect to see gradual changes for updated versions of the dataset. Another aspect that needs improvement is education, we observed that parents' education is important for immunization of children.

>>>>

## From results of analysis, what should be enhanced?
It clearly shows that Thailand, especially in the rural regions in 1987 required more health care infrastructure. As WHO reported that the Thailand government started investing more on primary health care services in the rural area in the 1980s, we expect to see gradual changes for updated versions of the dataset. Another aspect that needs improvement is education, we observed that parents' education is important for immunization of children, and considering that the significant number of mothers do not continue with their education after primary school, more investment in learning infrastructure should have been considered by the Thailand government. For better understanding of these issues, more detailed survey and research on healthcare and education infrastructure should be conducted.
